\newpage
\section{References}

\begingroup
\renewcommand{\section}[2]{}
\begin{thebibliography}{}
	\bibitem{Nordhagen}
	E. M. Nordhagen.
	Project 1 - FYS-STK4155 - Applied data analysis and machine learning.
	https://github.com/evenmn/FYS-STK4155/tree/master/doc/Project1.
	(2018).
	
	\bibitem{Marsland}
	S. Marsland.
	Machine Learning: An Algorithmic Perspective. Second Edition (Chapman \& Hall/Crc Machine Learning \& Pattern Recognition).
	(2014).
	
	\bibitem{Mehta}
	P. Mehta, C.H. Wang, A.G.R. Day, C. Richardson, M.Bukov, C.K.Fisher, D.J. Schwab.
	A high-bias, low-variance introduction to Machine Learning for physicists.
	(2018).
	
	\bibitem{AlexNet}
	ImageNet Classification with Deep Convolutional Neural Networks.
	A. Krizhevsky, I. Sutskever, G. E. Hinton.
	(2012).
	
	\bibitem{Hinton}
	K. Allen.
	How a Toronto professor’s research revolutionized artificial intelligence.
	thestar.com, retrieved November 3rd, 2018.
	(2015).
	
	\bibitem{Coin}
	Simulation stimulation.
	L. Bastick.
	https://www.sumproduct.com/thought/simulation-stimulation
	
	\bibitem{Berkeley}
	Machine Learning Crash Course: Part 4 - The Bias-Variance Dilemma.
	D. Geng, S. Shih.
	https://ml.berkeley.edu/blog/2017/07/13/tutorial-4/
	(2017).
	
	\bibitem{R2}
	Regression Analysis: How Do I Interpret R-squared and Assess the Goodness-of-Fit?
	http://blog.minitab.com/blog/adventures-in-statistics-2/regression-analysis-how-do-i-interpret-r-squared-and-assess-the-goodness-of-fit
	(2013).
	
	\bibitem{Bootstrap}
	Bootstrap Methods: Another Look at the Jackknife.
	B. Efron. 
	Ann. Statist., Volume 7, Number 1, 1-26.
	(1979).
	
	\bibitem{Lecture}
	Lecture notes FYS-STK4155: Regression Methods.
	https://compphysics.github.io/MachineLearning/doc/pub/Regression/pdf/Regression-minted.pdf
	M. Hjorth-Jensen.
	(2018).
	
	\bibitem{Scikit}
	Scikit-learn: Machine Learning in Python.
	F. Pedregosa, G. Varoquaux, A. Gramfort, V. Michel, B. Thiron, O. Grisel, M. Blondel, P. Prettenhofer, R. Weiss, V. Dubourg, J. Vanderplas, A. Passos, D. Cournapeau, M. Brucher, M. Perrot, E. Duchesnay.
    Journal of Machine Learning Research, Volume 12.
	(2011).
	
\end{thebibliography}
\endgroup