\newpage
\section{References}

\begingroup
\renewcommand{\section}[2]{}
\begin{thebibliography}{}
	\bibitem{Feloni}
	R. Feloni.
	20 years from now, regular people will have the personal assistants currently reserved for the rich and famous - through tech.
	\url{https://nordic.businessinsider.com/ai-assistants-will-run-our-lives-20-years-from-now-2018-1?r=US&IR=T}.
	(2018).
	
	\bibitem{Marsland}
	S. Marsland.
	Machine Learning: An Algorithmic Perspective. Second Edition (Chapman \& Hall/Crc Machine Learning \& Pattern Recognition).
	(2014).
	
	\bibitem{Mehta}
	P. Mehta, C.H. Wang, A.G.R. Day, C. Richardson, M.Bukov, C.K.Fisher, D.J. Schwab.
	A high-bias, low-variance introduction to Machine Learning for physicists.
	(2018).
	
	\bibitem{AlexNet}
	ImageNet Classification with Deep Convolutional Neural Networks.
	A. Krizhevsky, I. Sutskever, G. E. Hinton.
	(2012).
	
	\bibitem{Hinton}
	K. Allen.
	How a Toronto professor’s research revolutionized artificial intelligence.
	thestar.com, retrieved November 3rd, 2018.
	(2015).
	
	\bibitem{ELU}
	ELU-Networks: Fast and Accurate CNN Learning on ImageNet.
	M.Heusel, D.A.Clevert, G.Klambauer, A.Mayr, K.Schwarzbauer, T.Unterthiner, S.Hochreiter.
	http://image-net.org/challenges/posters/JKU\_EN\_RGB\_Schwarz\_poster.pdf
	
	\bibitem{logistic}
	Logistic Regression-Detailed Overview.
	S.Swaminathan.
	https://towardsdatascience.com/logistic-regression-detailed-overview-46c4da4303bc
	
	\bibitem{hjorth}
	Data Analysis and Machine Learning: Neural networks, from the simple perceptron to deep learning and convolutional networks.
	M.Hjorth-Jensen.
	https://compphysics.github.io/MachineLearning/doc/pub/NeuralNet/html/NeuralNet.html
	
\end{thebibliography}
\endgroup